Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores with Time Series Modeling

### 2020-01-23 Ben_Manuscripts/stochastic_transport/Final_Draft.tex
Incorporated MRS comments

\documentclass[aps,pre,preprint,groupedaddress]{revtex4-2}
\usepackage{CJK}

\usepackage{multirow}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{caption}
\usepackage{amsmath} % or simply amstext
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{xr}
\usepackage{diagbox}
\usepackage{array}

\DeclareUnicodeCharacter{03C9}{$\omega$}
\usepackage[english]{babel}

@@

  Lyotropic liquid crystals (LLCs) are a class of amphiphilic molecules that can be 
  cross-linked into mechanically strong and highly selective nanoporous membranes.~\cite{gin_polymerized_2008}
  They may provide a promising alternative to conventional membrane separation techniques
  by being selective based not only on solute size and charge, but on solute chemical 
  functionality as well.~\cite{dischinger_application_2017} One can tune the functionality
  of LLC monomers in order to enhance or weaken specific solute-membrane interactions.~\cite{dischinger_effect_2017}
  Two general morphologies of LLC membranes are being actively developed. The inverted hexagonal, 
  H\textsubscript{II}, LLC phase has densely packed, uniform-sized pores on the order of 1 nm
  in size. A perfectly synthesized H\textsubscript{II} phase has an ideal geometry for high
  throughput separations. 
  %MRS8: break sentence, tweak phrasing.
  %however 
  Unfortunately, aligning the microscopic hexagonal mesophases on a large 
  scale 
  as required for high permeability
  has shown limited success.~\cite{feng_scalable_2014,feng_thin_2016} Bicontinuous cubic,
  Q\textsubscript{I}, phase LLCs share the uniform and nm-sized chemically complex pores of
  the H\textsubscript{II} phase but its geometry consists of a tortuous network of 3D 
  interconnected pores which do not require alignment.~\cite{carter_glycerol-based_2012} While 
  its pore structure may decrease a Q\textsubscript{I} membrane's permeability relative to the
  H\textsubscript{II} phase, it is considerably easier to synthesize at scale.~\cite{hatakeyama_nanoporous_2010}

  Molecular modeling may make it possible to efficiently evaluate solute-specific separation
  membranes using the available chemical space of LLC monomers. To date, only a limited 
  subset of LLC monomers have been studied experimentally in membrane applications.
  %MRS6: should these references be contracted?
  %BJC6: probably, will see if that gets fixed by journal latex template
  \cite{carter_glycerol-based_2012,hatakeyama_nanoporous_2010,smith_ordered_1997,zhou_assembly_2003,resel_structural_2000}
  Even within this small subset, they have demonstrated selectivities that could not be
  explained beyond speculation and vague empirical correlations.~\cite{dischinger_application_2017}
  Atomistic molecular modeling can provide the resolution necessary to identify molecular 
  interactions that are key to separation mechanisms, allowing us to move beyond 
  Edisonian design approaches.

  In our previous work,~\cite{coscia_chemically_2019} we used molecular dynamics (MD) 
  simulations to study the transport of 20 small polar molecules in an H\textsubscript{II}
  phase LLC membrane.
  %MRS6: sentence seems out of place here? True, but does it support the thesis here?
  %BJC6: I said above how the QI phase is easier to synthesize, so I felt it necessary to 
  % quickly justify why we studied the HII phase. Reworded to make that clearer. I'm also open to
  % eliminating the sentence.
  %MRS6: It was also because they thought it was more likely to be interesting initially.  I'm in favor of 
  % cutting for simplicity. 
  We chose to study the H\textsubscript{II} phase because it is a simpler geometry to model than 
  the Q\textsubscript{I} phase
  %MRS8: added as more clarification
  and significantly more structural data is available to help ensure molecular models are consistent with experiment.
  In general, we observed subdiffusive transport behavior characterized by intermittent hops 
  separated by periods of entrapment. We identified three mechanisms responsible for the 
  solute trapping behavior: entanglement among monomer tails, hydrogen bonding with monomer
  head groups, and association with the monomer's sodium counter ions.

  %BJC4: Added next two paragraphs to help ease more into time series modeling
  Up through our previous studies, our molecular models have provided valuable 
  qualitative mechanistic insight with some quantitative support. This insight
  already allows us to speculate about new LLC monomer designs. However, they 
  would be of greater value to a larger set of researchers if we could provide 
  quantitative predictions of macroscopic observables such as solute flux and 
  selectivity. Due to the size of the types of systems we are studying (at least
  (62,000 atoms) it is prohibitively expensive and time-consuming to
  run simulations longer than those performed for this work ($\sim$5 $\mu$s). 
  Even with the relatively large size of our system, we only simulate 24 solute trajectories per unit cell in order
  to minimize solute-solute interactions. This results in relatively high uncertainties
  in observables such as mean squared displacement (MSD), preventing reliable long
  timescale predictions. We are in need of a way of studying the collective motion
  of a much larger set of solutes over much longer timescales.

  %BJC4: 1st paragraph moved to here
  Mathematical descriptions of transport in complex separations membranes are 
  a powerful way to understand mechanisms and formulate design principles. 
  \cite{vinh-thang_predictive_2013,geens_transport_2006,darvishmanesh_mass_2016}
  The complexity of a well-fit model generally parallels the complexity of the transport 
  mechanism being studied, as well as the transport information the model conveys.
  In dense homogeneous membranes, the solution-diffusion model can extract 
  diffusion and partition coefficients and has successfully predicted solute 
  transport rates.~\cite{wijmans_solution-diffusion_1995} Analogously, pore-flow
  models yield predictions of diffusion coefficients and solute transport rates 
  in nanoporous membranes.~\cite{paul_diffusive_1974} Modern single particle 
  tracking approaches have taken researchers beyond continuum modeling allowing them to 
  characterize complex diffusive behavior.~\cite{manzo_review_2015} At the molecular
  level, one can use molecular dynamics (MD) simulations to study both single 
  particle dynamics and bulk transport properties with atomic-level insight.~\cite{coscia_chemically_2019,maginn_best_2018}
  All of these approaches facilitate generation of hypotheses about the
  molecular origins of separations by attempting to give a more intuitive 
  understanding of how solutes move as a function of their environment, in turn
  suggesting experiments that could be performed.

  %BJC4: Tried to make this paragraph connect to previous a little better
  Using a bottom-up modeling approach, we can parameterize single particle behavior
  by extracting their trajectories from MD simulations and studying the properties that
  have the greatest influence on solute dynamics. With this information, we can learn
  how to construct an ensemble of characteristic single solute trajectories with these
  properties which would be useful for making long timescale predictions with computational
  ease and lower uncertainties. Fortunately, there is an abundance of information encoded
  in the complex solute trajectories. We can incorporate fluctuations and time-dependent 
  correlations in solute position as well as the length of time solutes are trapped into a
  model. We can add further
  detail by integrating our time series analysis with our knowledge of the primary
  trapping mechanisms as well as the solute's changing chemical environment within
  the heterogeneous membrane.

@@

  In this work, we use the output of our MD simulations to construct two classes of 
  mathematical models which aim to predict membrane performance while providing quantitative 
  mechanistic insights. The functional form of these models is driven by mechanistic 
  observations from our previous work and their inputs are parameterized using a 
  substantial amount of data generated by long ($\geq 5~\mu$s) MD simulations. 
  %MRS6: maybe rephrase the next - 'dive' is kind of casual?  Also, it seems more like the start of the next paragraph.
  %BJC6: I just got rid of the sentence. It doesn't really add anything
%  The formulation
%  of these models requires a dive into stochastically driven processes.

%  Our approach employs descriptive stochastic models that sufficiently
%  capture solute dynamics are capable of projecting long timescale transport behavior in addition to gaining a deeper understanding
%  of solute behavior on short timescales. In this work we explore two types of stochastic
%  models parameterized by our MD simulations.
%  
%  Unfortunately, the timescales that we can simulate with MD are insufficient to be
%  able to make well-converged predictions of macroscopic transport properties 
%  traditionally used to characterize membranes in the lab.
%  \begin{itemize}
%    \item However, if we use descriptive stochastic models that sufficiently capture solute
%    dynamics, then we could project long timescale behavior in addition to gaining
%    a deeper understanding of solute behavior on short timescales.
%  \end{itemize}

  %MRS4: consider more citations below, when you talk about what researchers have done.
  %BJC4: added citations of prominent anomalous diffusion work
  %BJC7: changed thesis to focus more on this paper
  We constructed our first model by applying the rigorous theoretical foundation 
  already developed to describe the motion of particles exhibiting non-Brownian, or
  anomalous, transport behavior.~\cite{metzler_random_2000,bouchaud_anomalous_1990}
  The tools introduced by fractional calculus are instrumental to this theory.~\cite{gorenflo_fractional_1997}
  They allow us to generalize the normally linear diffusion equation to fractional
  derivative orders, providing descriptions of a much more diverse set of behavior,
  including subdiffusion, a type of anomalous diffusion exhibited by solutes in 
  this study.~\cite{klages_anomalous_2008}

@@

  %BJC4: added mention of the anomalous subdiffusion model we chose 
%  Our first modeling approach is based on the anomalous diffusion literature, 
%  applying the mathematical formalism describing subdiffusive transport to observed
%  solute trajectories. Specifically, 
  %BJC7: with changes, above thesis statement is redundant
  We treated our system as an FBM process subordinate to a CTRW, or subordinated 
  FBM (sFBM) for short. We fit sFBM
  models in two ways: First, we parameterized solute motion using a single set of parameters fit
  to a hypothesized anomalous diffusion model. Second, we used a two-state approach
  by extracting two sets of model parameters calculated based on a solute's radial
  distance from the closest pore center. This allows us to include different dynamical
  behavior of solutes observed within the pore region versus within the monomer tails.

@@

%   is an elegant way to characterize single 
%  particle trajectories and in addition to providing an easy and efficient way to 
%  simulate solute trajectories, 
%  uncover the underlying solute-membrane interactions 
%  which result in observed transport mechanisms.

  % BJC7: moved last sentence of previous paragraph to here to make it more clear that
  % we are moving to a new model
  If one has knowledge of the primary mechanisms leading to anomalous diffusion behavior,
  one may gain additional insight by formulating a state-based model, such as Markov state
  models (MSMs). MSMs are a popular class of models used to project long timescale
  system properties based on molecular simulation trajectories by identifying
  different dynamical modes and quantifying the rates of transitions between them.
  MSMs are frequently used to study systems with slow dynamics, such as protein 
  folding.~\cite{snow_how_2005,chodera_automatic_2007} Researchers typically aim to 
  come up with a low dimensional representation of the system based on features 
  which preserve the process kinetics. This still often results in hundreds to thousands
  of distinct states.~\cite{chodera_markov_2014}

@@

  %BJC4: making goals more explicit
  We determine the degree of success of our modeling approaches in two ways. First,
  if we can closely reproduce solute MSDs measured from MD simulations with realizations
  of our models, then it is likely that the model sufficiently captures solute 
  dynamics and can be used in a predictive capacity. Even if a model fails to 
  reproduce the MD MSDs, there is value in uncovering the cause of the deviation.
  The second measure of success is by analysis of the parameters defining each 
  model. The parameters themselves should provide clues that help explain solute 
  dynamics in a coherent way. A model that successfully reproduces MD MSDs, but 
  with nonsensical parameters has severely diminished value as it could be a 
  consequence of over-fitting.

  % BJC4: new paragraph
  The goal of this work is not to definitively determine which modeling approach
  is better but to evaluate their performance independently because they both
  have potential value dependent on a given research study's goals. The anomalous subdiffusion
  approach provides a systematic way to compare the dynamical behavior of different
  solutes based solely on the time series of their center of mass positions. The process
  of choosing the correct anomalous subdiffusion provides its own mechanistic insight
  since it requires a thorough analysis of solute time series behavior. One can simulate
  different solutes, compare the fit model parameters and relate them back to 
  differences in solute size and chemical composition. 
  %MRS8: this may be a bit of a stretch, since it's not clear it helps that much in the end, but 
  %is fine to leave in now - maybe we revisit if needed during revisions.
  The MSDDM characterizes 
  explicitly defined trapping mechanisms, providing a clear picture of solute behavior
  while in each trapped state as well as the equilibrium occupation of each trapping state.
  It is possible to use the two models in tandem, the anomalous diffusion model to
  identify mechanisms, and the MSDDM to characterize mechanisms.

@@

%  We find that the sFBM anomalous diffusion model does the best job of reproducing
%  simulation behavior of all solutes studied. Therefore, we use it to demonstrate 
%  how one could predict solute flux through a theoretical pore of with an 
%  experimentally relevant length.

%  It is our goal to reproduce
%  the mean squared displacements (MSDs) exhibited by each solute on MD timescales and
%  then to project the long-term dynamics of each solute. We can gain further
%  mechanistic insight by studying the parameters of each model. 
  %BJC3: need to decide value in long term projections

@@

  We ran all MD simulations and energy minimizations using GROMACS 2018~\cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}.  %BJC4: version 2018. That's it not 2018.3 or anything. 
  We performed all post-simulation trajectory analysis using Python scripts which 
  are available online at \\ \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.
  The appropriate scripts to use for subsequent calculations are summarized in 
  Table~\ref{S-table:python_scripts} of the Supporting Information.

@@

  We studied transport of solutes in the H\textsubscript{II} phase using an atomistic
  molecular model of four pores in a monoclinic unit cell with 10\% water by weight 
  (see Figure~\ref{fig:membrane_structure}). Approximately one third of the water 
  molecules occupy the tail region with the rest near the pore center. We chose to
  focus our study on the 10 wt\% water system because solutes move significantly 
  faster than in the 5 wt\% system studied previously thus allowing more statistically
  valid analyses.
%  . Appropriate stochastic 
%  modeling requires that solutes sample the accessible mechanisms with representative
%  probability.

  \begin{figure}
  \centering
  \begin{subfigure}{0.4\textwidth}
  \centering
  \includegraphics[width=\textwidth]{NaGA3C11.pdf}
  \caption{}\label{fig:monomer_structure}
  \end{subfigure}
  \begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=0.5\textwidth]{membrane_profile.pdf}
  \caption{}\label{fig:membrane_profile}
  \end{subfigure}
  \caption{(a) The wedge-shaped liquid crystal monomer Na-GA3C11 will form the inverted
  hexagonal phase in the presence of water where the carboxylate head groups occupy the
  pore centers. (b) A cross-section of a periodically replicated atomistic unit cell 
  used for simulations in this study reveals the membrane's aqueous, hexagonally packed,
  straight and uniform sized pores. Water present in the tail region is omitted 
  for clarity.}\label{fig:membrane_structure}
  %MRS8: should say something about the molecular colors for (b) so it's clear what is what. 
  \end{figure}

%  \begin{figure}
%  \centering
%  \subfloat[\label{fig:monomer_structure}]{%
%  			\includegraphics[width=0.4\textwidth, valign=c]{NaGA3C11.pdf}%
%  			\vphantom{\includegraphics[width=0.5\textwidth, valign=c]{membrane_profile.pdf}}
%  			}\hfill
%  \subfloat[\label{fig:membrane_profile}]{\includegraphics[width=0.5\textwidth, valign=c]{membrane_profile.pdf}}\hfill
%  \caption{(a) The wedge-shaped liquid crystal monomer Na-GA3C11 will form the inverted
%  hexagonal phase in the presence of water where the carboxylate head groups occupy the
%  pore centers. (b) A cross-section of a periodically replicated atomistic unit cell 
%  used for simulations in this study reveals the membrane's aqueous, hexagonally packed,
%  straight and uniform sized pores. Water present in the tail region is omitted 
%  for clarity.}\label{fig:membrane_structure}
%  \end{figure}

  We chose to study a subset of the 4 fastest moving solutes from our previous
  work: methanol, acetic acid, urea and ethylene glycol. For each solute we 
  created a separate system and to each system we added 6 solutes per pore 
  for a total of 24 solutes. On the time scales which we simulate, this number
  of solutes per pore provides a a sufficient amount of data from which to 
  generate statistics. It also maintains a low degree of interaction between
  solutes since, at present, we are primarily interested in solute-membrane 
  interactions.
%  balance
%  of a low degree of interaction between solutes, since we are primarily interested 
%  in solute-membrane interactions at present, as well as a sufficient amount of 
%  data from which to generate statistics on the time scales which we simulate.
  Further details on the setup and equilibration of these systems are described in
  our previous work.\cite{coscia_chemically_2019}

@@

  We considered each system to be equilibrated when the solute partitioning between the 
  pore and tail region reached apparent equilibrium and use only data after that point
  in our analysis of solute kinetics. We plot the solute partition versus time in
  Figure~\ref{S-fig:equilibration} of the Supporting Information in order to justify
  our choice of equilibration times for each solute.

@@

  %BJC7: added following two paragraphs to clarify our usage of the MSD as a tool. Modified a bit below too  
  While it is theoretically possible to extract the value of $\alpha$ by fitting
  Equation~\ref{eqn:msd_form} to an MSD generated directly from MD simulations, 
  we do not simulate enough independent solute trajectories to obtain a reliable
  estimate. We can obtain higher precision estimates of $\alpha$ using the dwell
  time distributions described in subsequent sections.

  %MRS8: some tweaks

  In this study, we primarily use the MSD as a tool for characterizing
  the average dynamic behavior solute trajectories. Rather than using
  them to calculate diffusion constants or to relate our simulations
  to experimental measurement, we compare MSDs calculated from MD
  simulations to those generated from our models in order to validate
  those models. Therefore, it is only important that we use a
  consistent definition for calculating the MSD between modeled
  trajectories and directly observed MD trajectories.

@@

%  For a small number of solute 
%  trajectories, this is a much more statistically robust measure of the 
%  average distance a solute travels over time.

@@

  We chose to 
  %MRS8: tweaked.
  %analyze 
  use 
  just the time-averaged MSD 
  to compare MD trajectory and modeled trajectories,
  because, compared to the ensemble
  average, it is a more statistically robust measure of the average distance a 
  solute travels over time. The ensemble MSD of only 24 solute trajectories would
  have much higher uncertainties.

%  It may be difficult to calculate  ensemble
%  MSD to estimate $\alpha$ with only 24 solute trajectories.
%  
%  Although theoretically possible, we do not use the 
%  ensemble averaged MSD to calculate $\alpha$ because we can extract the same 
%  parameter with higher precision using the dwell time distributions as described below.

@@

%  BJC4: I say something to the following effect in the intro
%  The solute motion in the system studied here may be consistent with 
%  subordinated fractional Brownian motion (sFBM) where the parent process is FBM and 
%  the leading process is a CTRW. We observe hopping and trapping which is consistent
%  with a CTRW, along with negatively correlated hops which is consistent with FBM.

%  We modeled solute motion as a continuous time random walk (CTRW) subordinate to 
%  fractional Brownian motion, also called subordinated fractional Brownian motion (sFBM).
%  We modeled solute motion as a CTRW subordinate to FBM, also called sFBM.

@@

  In practical applications, the heavy tail of power law distributions can result in 
  arbitrarily long dwell times that are never observed in MD simulations. 
  %We cannot observe dwell times longer than the length of a single trajectory. 
  In order to directly compare our anomalous diffusion model to finite-length MD 
  trajectories we need to bound the dwell time distribution. A standard way of 
  doing this, with easily estimated parameters, is by adding an exponential 
  cut-off to the power law so the dwell time distribution is now proportional 
  to $t^{-1 - \alpha}e^{-\lambda t}$.~\cite{newman_power_2005,clauset_power-law_2009}  % Clauset uses data from other papers and gives a bunch of example where the cut-off is the most favorable model. 
  %MRS6: are there papers to cite that this is a standard way to cut them off (i.e. rather than truncate, etc).
  % of the form:
%  \begin{equation}  %BJC3: maybe make this equation in line? Else move regular power law to its own equation
%    p(t) \propto t^{-1 - \alpha}e^{-\lambda t}
%  \label{eqn:powerlaw_cutoff}
%  \end{equation}
  We determine MLEs of $\alpha$ and $\lambda$ by maximizing the likelihood function:~\cite{clauset_power-law_2009}
  \begin{equation}
    \mathcal{L}(\alpha, \lambda) = n(1 - \alpha)\ln\lambda - n\ln\Gamma(1 - \alpha, t_{min}\lambda) - \alpha\sum_{i=1}^{n}\ln t_i - \lambda\sum_{i=1}^n t_i
  \label{eqn:powerlaw_cutoff_likelihood}
  \end{equation}

@@

%  We observed negatively correlated hops within each state and among transitions between
%  states. We can use the Hurst parameter to describe this negative time series correlation
%  however, there is not sufficient data to accurately measure a Hurst parameter for 
%  each type of transition. We avoided this problem by treating transitions as correlated
%  emissions from a single L\'evy stable distribution. This reduces the number of emission
%  distributions from 64 to 9 (1 for each state and 1 for transitions between states).

@@

%  corresponding emissions from the rows of the probability transition matrix and the 
%  appropriate emission distribution respectively. We added correlation between transitions
%  as well as to sequences of emissions while dwelling in specific states using the FLM
%  simulation procedure described in Section~\ref{method:model_sFBM}.

>>>>

\documentclass[aps,pre,preprint,groupedaddress,longbibliography]{revtex4-2}
\usepackage{CJK}

\usepackage{multirow}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
%\usepackage{caption}
\usepackage{amsmath} % or simply amstext
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{xr}
\usepackage{diagbox}
\usepackage{array}

\DeclareUnicodeCharacter{03C9}{$\omega$}
%\usepackage[en]{babel}

@@

  Lyotropic liquid crystals (LLCs) are a class of amphiphilic molecules that can be 
  cross-linked into mechanically strong and highly selective nanoporous membranes.~\cite{gin_polymerized_2008}
  They may provide a promising alternative to conventional membrane separation techniques
  by being selective based not only on solute size and charge, but on solute chemical 
  functionality as well.~\cite{dischinger_application_2017} One can tune the functionality
  of LLC monomers in order to enhance or weaken specific solute-membrane interactions.~\cite{dischinger_effect_2017}
  Two general morphologies of LLC membranes are being actively developed. The inverted hexagonal, 
  H\textsubscript{II}, LLC phase has densely packed, uniform-sized pores on the order of 1 nm
  in size. A perfectly synthesized H\textsubscript{II} phase has an ideal geometry for high
  throughput separations. Unfortunately, aligning the microscopic hexagonal mesophases on 
  a large scale as required for high permeability has shown limited success.~\cite{feng_scalable_2014,feng_thin_2016} Bicontinuous cubic,
  Q\textsubscript{I}, phase LLCs share the uniform and nm-sized chemically complex pores of
  the H\textsubscript{II} phase but its geometry consists of a tortuous network of 3D 
  interconnected pores which do not require alignment.~\cite{carter_glycerol-based_2012} While 
  its pore structure may decrease a Q\textsubscript{I} membrane's permeability relative to the
  H\textsubscript{II} phase, it is considerably easier to synthesize at scale.~\cite{hatakeyama_nanoporous_2010}

  Molecular modeling may make it possible to efficiently evaluate solute-specific separation
  membranes using the available chemical space of LLC monomers. To date, only a limited 
  subset of LLC monomers have been studied experimentally in membrane applications.
  \cite{carter_glycerol-based_2012,hatakeyama_nanoporous_2010,smith_ordered_1997,zhou_assembly_2003,resel_structural_2000}
  Even within this small subset, they have demonstrated selectivities that could not be
  explained beyond speculation and vague empirical correlations.~\cite{dischinger_application_2017}
  Atomistic molecular modeling can provide the resolution necessary to identify molecular 
  interactions that are key to separation mechanisms, allowing us to move beyond 
  Edisonian design approaches.

  In our previous work,~\cite{coscia_chemically_2019} we used molecular dynamics (MD) 
  simulations to study the transport of 20 small polar molecules in an H\textsubscript{II}
  phase LLC membrane. We chose to study the H\textsubscript{II} phase because it is
  a simpler geometry to model than the Q\textsubscript{I} phase and significantly more
  structural data is available to help ensure molecular models are consistent with experiment.
  In general, we observed subdiffusive transport behavior characterized by intermittent hops 
  separated by periods of entrapment. We identified three mechanisms responsible for the 
  solute trapping behavior: entanglement among monomer tails, hydrogen bonding with monomer
  head groups, and association with the monomer's sodium counter ions.

  Up through our previous studies, our molecular models have provided valuable 
  qualitative mechanistic insight with some quantitative support. This insight
  already allows us to speculate about new LLC monomer designs. However, they 
  would be of greater value to a larger set of researchers if we could provide 
  quantitative predictions of macroscopic observables such as solute flux and 
  selectivity. Due to the size of the types of systems we are studying (at least
  (62,000 atoms) it is prohibitively expensive and time-consuming to
  run simulations longer than those performed for this work ($\sim$5 $\mu$s). 
  Even with the relatively large size of our system, we only simulate 24 solute trajectories per unit cell in order
  to minimize solute-solute interactions. This results in relatively high uncertainties
  in observables such as mean squared displacement (MSD), preventing reliable long
  timescale predictions. We are in need of a way of studying the collective motion
  of a much larger set of solutes over much longer timescales.

  Mathematical descriptions of transport in complex separations membranes are 
  a powerful way to understand mechanisms and formulate design principles. 
  \cite{vinh-thang_predictive_2013,geens_transport_2006,darvishmanesh_mass_2016}
  The complexity of a well-fit model generally parallels the complexity of the transport 
  mechanism being studied, as well as the transport information the model conveys.
  In dense homogeneous membranes, the solution-diffusion model can extract 
  diffusion and partition coefficients and has successfully predicted solute 
  transport rates.~\cite{wijmans_solution-diffusion_1995} Analogously, pore-flow
  models yield predictions of diffusion coefficients and solute transport rates 
  in nanoporous membranes.~\cite{paul_diffusive_1974} Modern single particle 
  tracking approaches have taken researchers beyond continuum modeling allowing them to 
  characterize complex diffusive behavior.~\cite{manzo_review_2015} At the molecular
  level, one can use molecular dynamics (MD) simulations to study both single 
  particle dynamics and bulk transport properties with atomic-level insight.~\cite{coscia_chemically_2019,maginn_best_2018}
  All of these approaches facilitate generation of hypotheses about the
  molecular origins of separations by attempting to give a more intuitive 
  understanding of how solutes move as a function of their environment, in turn
  suggesting experiments that could be performed.

  Using a bottom-up modeling approach, we can parameterize single particle behavior
  by extracting their trajectories from MD simulations and studying the properties that
  have the greatest influence on solute dynamics. With this information, we can learn
  how to construct an ensemble of characteristic single solute trajectories with these
  properties which would be useful for making long timescale predictions with computational
  ease and lower uncertainties. Fortunately, there is an abundance of information encoded
  in the complex solute trajectories. We can incorporate fluctuations and time-dependent 
  correlations in solute position as well as the length of time solutes are trapped into a
  model. We can add further detail by integrating our time series analysis with our 
  knowledge of the primary trapping mechanisms as well as the solute's changing chemical
  environment within the heterogeneous membrane.

@@

  In this work, we use the output of our MD simulations to construct two classes of 
  mathematical models which aim to predict membrane performance while providing quantitative 
  mechanistic insights. The functional form of these models is driven by mechanistic 
  observations from our previous work and their inputs are parameterized using a 
  substantial amount of data generated by long ($\geq 5~\mu$s) MD simulations.

  We constructed our first model by applying the rigorous theoretical foundation 
  already developed to describe the motion of particles exhibiting non-Brownian, or
  anomalous, transport behavior.~\cite{metzler_random_2000,bouchaud_anomalous_1990}
  The tools introduced by fractional calculus are instrumental to this theory.~\cite{gorenflo_fractional_1997}
  They allow us to generalize the normally linear diffusion equation to fractional
  derivative orders, providing descriptions of a much more diverse set of behavior,
  including subdiffusion, a type of anomalous diffusion exhibited by solutes in 
  this study.~\cite{klages_anomalous_2008}

@@

  We treated our system as an FBM process subordinate to a CTRW, or subordinated 
  FBM (sFBM) for short. We fit sFBM
  models in two ways: First, we parameterized solute motion using a single set of parameters fit
  to a hypothesized anomalous diffusion model. Second, we used a two-state approach
  by extracting two sets of model parameters calculated based on a solute's radial
  distance from the closest pore center. This allows us to include different dynamical
  behavior of solutes observed within the pore region versus within the monomer tails.

@@

  If one has knowledge of the primary mechanisms leading to anomalous diffusion behavior,
  one may gain additional insight by formulating a state-based model, such as Markov state
  models (MSMs). MSMs are a popular class of models used to project long timescale
  system properties based on molecular simulation trajectories by identifying
  different dynamical modes and quantifying the rates of transitions between them.
  MSMs are frequently used to study systems with slow dynamics, such as protein 
  folding.~\cite{snow_how_2005,chodera_automatic_2007} Researchers typically aim to 
  come up with a low dimensional representation of the system based on features 
  which preserve the process kinetics. This still often results in hundreds to thousands
  of distinct states.~\cite{chodera_markov_2014}

@@

  We determine the degree of success of our modeling approaches in two ways. First,
  if we can closely reproduce solute MSDs measured from MD simulations with realizations
  of our models, then it is likely that the model sufficiently captures solute 
  dynamics and can be used in a predictive capacity. Even if a model fails to 
  reproduce the MD MSDs, there is value in uncovering the cause of the deviation.
  The second measure of success is by analysis of the parameters defining each 
  model. The parameters themselves should provide clues that help explain solute 
  dynamics in a coherent way. A model that successfully reproduces MD MSDs, but 
  with nonsensical parameters has severely diminished value as it could be a 
  consequence of over-fitting.

  The goal of this work is not to definitively determine which modeling approach
  is better but to evaluate their performance independently because they both
  have potential value dependent on a given research study's goals. The anomalous subdiffusion
  approach provides a systematic way to compare the dynamical behavior of different
  solutes based solely on the time series of their center of mass positions. The process
  of choosing the correct anomalous subdiffusion provides its own mechanistic insight
  since it requires a thorough analysis of solute time series behavior. One can simulate
  different solutes, compare the fit model parameters and relate them back to 
  differences in solute size and chemical composition. 
  %MRS8: this may be a bit of a stretch, since it's not clear it helps that much in the end, but 
  %is fine to leave in now - maybe we revisit if needed during revisions.
  The MSDDM characterizes 
  explicitly defined trapping mechanisms, providing a clear picture of solute behavior
  while in each trapped state as well as the equilibrium occupation of each trapping state.
  It is possible to use the two models in tandem, the anomalous diffusion model to
  identify mechanisms, and the MSDDM to characterize mechanisms.

@@

@@

  We ran all MD simulations and energy minimizations using GROMACS 2018~\cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}.  %BJC4: version 2018. That's it not 2018.3 or anything. 
  We performed all post-simulation trajectory analysis using Python scripts which 
  are available online at \\ \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.
  The appropriate scripts to use for subsequent calculations are summarized in 
  Table~\ref{S-table:python_scripts} of the Supplemental Material.

@@

  We studied transport of solutes in the H\textsubscript{II} phase using an atomistic
  molecular model of four pores in a monoclinic unit cell with 10\% water by weight 
  (see Figure~\ref{fig:membrane_structure}). Approximately one third of the water 
  molecules occupy the tail region with the rest near the pore center. We chose to
  focus our study on the 10 wt\% water system because solutes move significantly 
  faster than in the 5 wt\% system studied previously thus allowing more statistically
  valid analyses.

  \begin{figure}
  \centering
  \begin{subfigure}{0.4\textwidth}
  \centering
  \vspace{1.1cm}
  \includegraphics[width=\textwidth]{NaGA3C11.pdf}
  \vspace{0.6cm}
  \caption{}\label{fig:monomer_structure}
  \end{subfigure}
  \begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=\textwidth]{membrane_profile.pdf}
  \caption{}\label{fig:membrane_profile}
  \end{subfigure}
  \caption{(a) The wedge-shaped liquid crystal monomer Na-GA3C11 will form the inverted
  hexagonal phase in the presence of water where the carboxylate head groups occupy the
  pore centers. (b) A cross-section of a periodically replicated atomistic unit cell 
  used for simulations in this study reveals the membrane's aqueous, hexagonally packed,
  straight and uniform sized pores. Water molecules (red and white spheres) present in 
  the tail region are omitted for clarity.}\label{fig:membrane_structure}
  \end{figure}

  We chose to study a subset of the 4 fastest moving solutes from our previous
  work: methanol, acetic acid, urea and ethylene glycol. For each solute we 
  created a separate system and to each system we added 6 solutes per pore 
  for a total of 24 solutes. On the time scales which we simulate, this number
  of solutes per pore provides a sufficient amount of data from which to 
  generate statistics. It also maintains a low degree of interaction between
  solutes since, at present, we are primarily interested in solute-membrane 
  interactions. Further details on the setup and equilibration of these systems
  are described in our previous work.\cite{coscia_chemically_2019}

@@

  We considered each system to be equilibrated when the solute partitioning between the 
  pore and tail region reached apparent equilibrium and use only data after that point
  in our analysis of solute kinetics. We plot the solute partition versus time in
  Figure~\ref{S-fig:equilibration} of the Supplemental Material in order to justify
  our choice of equilibration times for each solute.

@@

  While it is theoretically possible to extract the value of $\alpha$ by fitting
  Equation~\ref{eqn:msd_form} to an MSD generated directly from MD simulations, 
  we do not simulate enough independent solute trajectories to obtain a reliable
  estimate. We can obtain higher precision estimates of $\alpha$ using the dwell
  time distributions described in subsequent sections.

  In this study, we primarily use the MSD as a tool for characterizing the average
  dynamic behavior of solute trajectories. Rather than using them to calculate 
  diffusion constants or to relate our simulations to experimental measurement, we
  compare MSDs calculated from MD simulations to those generated from our models 
  in order to validate those models. Therefore, it is only important that we use a
  consistent definition for calculating the MSD between modeled trajectories and
  directly observed MD trajectories.

@@

@@

  We chose to use just the time-averaged MSD to compare MD trajectory and modeled
  trajectories, because, compared to the ensemble average, it is a more 
  statistically robust measure of the average distance a solute travels over time.
  The ensemble MSD of only 24 solute trajectories would have much higher uncertainties.

@@

@@

  In practical applications, the heavy tail of power law distributions can result in 
  arbitrarily long dwell times that are never observed in MD simulations. 
  In order to directly compare our anomalous diffusion model to finite-length MD 
  trajectories we need to bound the dwell time distribution. A standard way of 
  doing this, with easily estimated parameters, is by adding an exponential 
  cut-off to the power law so the dwell time distribution is now proportional 
  to $t^{-1 - \alpha}e^{-\lambda t}$.~\cite{newman_power_2005,clauset_power-law_2009}  % Clauset uses data from other papers and gives a bunch of example where the cut-off is the most favorable model. 
  We determine MLEs of $\alpha$ and $\lambda$ by maximizing the likelihood function:~\cite{clauset_power-law_2009}
  \begin{equation}
    \mathcal{L}(\alpha, \lambda) = n(1 - \alpha)\ln\lambda - n\ln\Gamma(1 - \alpha, t_{min}\lambda) - \alpha\sum_{i=1}^{n}\ln t_i - \lambda\sum_{i=1}^n t_i
  \label{eqn:powerlaw_cutoff_likelihood}
  \end{equation}

@@

@@
